On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-13 Manuscript/manuscript.tex

Block bootstrap preserves the serial dependence in the observed data by
partitioning the data into blocks and performing bootstrap on the blocks.
In particular, consider block size~$l$ and, for convenience, suppose that
$n$ is a multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$
is $Y_j = \{X_{(j - 1) * l + 1}, \ldots, X_{(j - 1) * l + l}\}$,
$j = 1, \ldots,   k$.  Then, we sample $k$ blocks of $Y_j$'s from the set 
$\{Y_1, \ldots, Y_k\}$ with replacement and concatenate the $k$ sampled blocks
in the order they are picked to form a bootstrap sample of the data. The
formation of the bootstrap sample ensures that the between-block dependence is
weak and that the within-block serial dependence is preserved. Because the
blocks here are non-overlapping, this bootstrap approach is known as
non-overlapping block bootstrap, or simple block bootstrap.

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then align them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$) as:
\jy{Any equation must be a part of a sentence and should be punctuated.}
\jy{Recall a blank line means a new paragraph.}
\jy{Define your response command with color and respond}
\mc{addressed above comments}
\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\} & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation}
\jy{The ending index does not seem right}
\mc{addressed above}
The second version of moving block bootstrap was used in
this study because it is the implementation provided in the function
\texttt{tsboot} from R package \textsl{boot} \citep{boot}, and it is easier
overall because $l$ need not divide $n$.
\jy{state we use it because it is implemented in package boot and cite boot}  
\jy{This reference is from a low-tier journal. Find something from a stronger
  journal?}
\mc{addressed above comments}
The block size~$l$ needs to chosen with care. It needs to be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be some variability between each bootstrap sample. As $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}, which is how the value of $l$ was determined for
this
study. It may be worth investigating in a future study if another block size
scheme is 
optimal for the context of a time series by comparing different block sizes
whilst keeping the sample size fixed.

@@

\jy{can we give references to each of the method? How about the review paper in
  Statistical Science?}
\mc{references for percentile and BCA, couldn't find for centered, standard,
  or student's t}

>>>>

Block bootstrap preserves the serial dependence in the observed data by
partitioning the data into blocks and performing bootstrap on the blocks.
In particular, consider block size~$l$ and, for convenience, suppose that
$n$ is a multiple of $l$ such that there are $k = n / l$ blocks. Each block~$j$
is $Y_j = \{X_{(j - 1) l + 1}, \ldots, X_{(j - 1) l + l}\}$,
$j = 1, \ldots,   k$.  Then, we sample $k$ blocks of $Y_j$'s from the set 
$\{Y_1, \ldots, Y_k\}$ with replacement and concatenate the $k$ sampled blocks
in the order they are picked to form a bootstrap sample of the data. The
formation of the bootstrap sample ensures that the between-block dependence is
weak and that the within-block serial dependence is preserved. Because the
blocks here are non-overlapping, this bootstrap approach is known as
non-overlapping block bootstrap, or simple block bootstrap.

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then align them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$) as:
\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation}
The wrap-around version does not require that $n/l$ be an integer.
We used this version in this study as implemented in the function
\texttt{tsboot} from R package \textsl{boot} \citep{boot}.

The block size~$l$ needs to be chosen with care. It should be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be a large number of blocks to give sufficient variability between
each bootstrap sample. As $n$ increases, both~$l$
and $n / l$ should also increase. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered optimal is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}, which was adopted in this
study. It may be worth investigating in a future study if another block size
scheme is \jy{Seems out of place. Maybe in the discussion section.}
optimal for the context of a time series by comparing different block sizes
whilst keeping the sample size fixed.

@@

\jy{order them as we discussed.}
